Are you moving predictably?

### 2018-07-16 dokumentation/MiriamClustering.tex
Miriam hat keine Lust mehr

%Timo hat fineliner
%oder doch eilaina
In the first step we try to cluster the \textit{Original Data} in \textit{6 Cluster}. Therefore we retrieve the original data set in RapidMiner and choose k as 6.

@@

\Cref{fig:OrgDist} is the result of the first try. \Cref{fig:OrgSt} shows the strata distribution as pie chart and \Cref{fig:OrgCl} the resulted cluster distribution. It can already been seen, that the distributions are not similar. For more steps the outcome is analogous.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.5\textwidth]{ClusterOrigRapidDistribution2Cluster.PNG}
\caption{Distribution of the clusters in between the grouped strata}
\label{fig:Groupdist}
\end{figure}
%#ArschFuerNachbarn
%#BloederKommentar
%#0:15

@@

\begin{figure}[!htbp]
\vspace{-3em}
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{ClusterOrigRapidDistribution2038eq.PNG}
\caption{For 6 clusters}
\label{fig:2038_6}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{ClusterOrigRapidDistribution2038eq2.PNG}
\caption{For 3 clusters}
\label{fig:2038_3}
\end{subfigure}
\caption{Distribution of the clusters in between the strata dataset size 2038}
\label{fig:2038_Clust}
\vspace{-3em}
\end{figure}
\vspace{-3em}
\begin{figure}[H]
	\vspace{-3em}
	\centering
	\begin{subfigure}{.43\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{vectorclusteringcluster.PNG}
		\caption{Strata}
		\label{fig:VecSt}
	\end{subfigure}%
	\begin{subfigure}{.4\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{vectorclusteringstrata.PNG}
		\caption{Cluster}
		\label{fig:VecCl}
	\end{subfigure}
	\caption{Distribution of stratified person data}
	\label{fig:VecDist}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{vectorclusteringcluster1000.PNG}
	\includegraphics[width=0.49\textwidth]{vectorClustering1000.PNG}
	\caption{1000 steps clustering in 6 clusters on maximal stratified person dataset}
	\label{fig:1000vect}
\end{figure}

Different dataset sizes and equal distribution of the stratas do not effect the result. In  \Cref{fig:2038_Clust} two clustering results can be seen. Again we could not observe a significant correlation.

After those not convincing results we applied the process to the \textit{stratified person data}.

The results for the whole data set without equalization are shown in \Cref{fig:2038_Clust}. We change the number of steps to 1000 for comparison and the result, illustrated in \Cref{fig:1000vect}, lets us assume, that 3 clusters would fit better.

\begin{figure}[H]
\centering
\includegraphics[width=0.69\textwidth]{vectorClustering31000.PNG}
\caption{1000 steps clustering in 3 clusters on maximal stratified person dataset}
\label{fig:1000vect3}
\end{figure}

\Cref{fig:1000vect3} shows clearly, that again no correlation can be found. Applying the procedure to the different datasets we generate similar results.

%PCA?
To save time we apply the PCA process on the \textit{original data} without strata and a variance
threshold of 0.95. We get two Attributes, so we can assume, that the data is strongly correlated. As expected the computing time decreases a lot for the whole process of clustering.

\begin{figure}[H]
\vspace*{-1em}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidStrata.PNG}
  \caption{Strata}
  \label{fig:PCAOrgSt}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster.PNG}
  \caption{Cluster}
  \label{fig:PCAOrgCl}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster2Cluster.PNG}
  \caption{3Cluster}
  \label{fig:PCAOrgCl3}
\end{subfigure}
\caption{Distribution of original data}
\label{fig:PCAOrgDist}
\vspace*{-2em}
\end{figure}

For a clustering of 6 clusters we get a distribution, which can be seen in \Cref{fig:PCAOrgDist}, similar to the one we get from the k-means process with the same configurations. 
For a clustering of 3 clusters we again get results, that are unclear(\Cref{fig:PCAOrgCl3}).

>>>>

%Timo hat fineliner
%oder doch eilaina
In the first step we try to cluster the \textit{Original Data} in \textit{6 cluster}. Therefore we retrieve the original data set in RapidMiner and choose $k$ as 6.

@@

\Cref{fig:OrgDist} is the result of the first try represented as pie charts. \Cref{fig:OrgSt} shows the strata distribution and \Cref{fig:OrgCl} the resulted cluster distribution. It can already been seen, that the distributions are not similar. For more steps the outcome is analogous.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.5\textwidth]{ClusterOrigRapidDistribution2Cluster.PNG}
\caption{Distribution of the clusters within the grouped strata}
\label{fig:Groupdist}
\end{figure}
%#ArschFuerNachbarn
%#BloederKommentar
%#0:15

@@

\begin{figure}[!htbp]
\vspace{-3em}
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{ClusterOrigRapidDistribution2038eq.PNG}
\caption{For 6 clusters}
\label{fig:2038_6}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{ClusterOrigRapidDistribution2038eq2.PNG}
\caption{For 3 clusters}
\label{fig:2038_3}
\end{subfigure}
\caption{Distribution of the clusters in between the strata dataset size 2038}
\label{fig:2038_Clust}
\vspace{-3em}
\end{figure}
\vspace{-3em}
\begin{figure}[H]
	\vspace{-3em}
	\centering
	\begin{subfigure}{.43\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{vectorclusteringcluster.PNG}
		\caption{Strata}
		\label{fig:VecSt}
	\end{subfigure}%
	\begin{subfigure}{.4\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{vectorclusteringstrata.PNG}
		\caption{Cluster}
		\label{fig:VecCl}
	\end{subfigure}
	\caption{Distribution of stratified person data}
	\label{fig:VecDist}
\end{figure}
\vspace*{-3em}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{vectorclusteringcluster1000.PNG}
	\includegraphics[width=0.49\textwidth]{vectorClustering1000.PNG}
	\caption{1000 steps clustering in 6 clusters on maximal stratified person dataset}
	\label{fig:1000vect}
\end{figure}
\vspace*{-2em}

Different dataset sizes and equal distribution of the stratas do not effect the result. In  \Cref{fig:2038_Clust} the clustering results for the maximal sized dataset can be seen. Once aggregated and once normal. Again we could not observe a significant correlation.

After those not convincing results, we apply the process to the \textit{stratified person data}.

The results for the whole data set without equalization are shown in \Cref{fig:VecDist}. We change the number of steps to 1000 for comparison and the result, illustrated in \Cref{fig:1000vect}, lets us assume, that 3 clusters would fit better.

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{vectorClustering31000.PNG}
\caption{1000 steps clustering in 3 clusters on maximal stratified person dataset}
\label{fig:1000vect3}
\end{figure}

\Cref{fig:1000vect3} shows clearly, that again no correlation can be found. Applying the procedure to the different datasets, we generate similar results.

%PCA?
To save time, we apply the PCA process on the \textit{original data} without strata and a variance
threshold of 0.95. We get two attributes, so we can assume, that the data is strongly correlated. As expected the computing time decreases a lot for the whole process of clustering.

\begin{figure}[H]
\vspace*{-1em}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidStrata.PNG}
  \caption{Strata}
  \label{fig:PCAOrgSt}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster.PNG}
  \caption{6 cluster}
  \label{fig:PCAOrgCl}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster2Cluster.PNG}
  \caption{3 cluster}
  \label{fig:PCAOrgCl3}
\end{subfigure}
\caption{Distributions of the original data. Clustering with the PCA process}
\label{fig:PCAOrgDist}
\vspace*{-2em}
\end{figure}

For the clustering with the preprocessing step PCA, we get distributions, which can be seen in \Cref{fig:PCAOrgDist}, similar to the distributions we get from the k-means process with the same configurations. 
For a clustering of 3 clusters we again get results, that are not meaningful (\Cref{fig:PCAOrgCl3}).

### 2018-07-16 dokumentation/conclusion.tex
Miriam hat keine Lust mehr

	\section{Discussion} \label{sec: discussion}
%	\begin{itemize}
%		\item repr. working day
%		\item over/under std's
%		\item indiv. of lifestyle
%		\item inv. behaviour in same strata
%	\end{itemize}
	Regarding the results, of not predicting the strata and also not observing any meaningful clusters throughout the data in given and stratified form, we thought about various aspects having an impact on the movement. We state 4 main influencing aspects, explaining the variance throughout the data.

	\subsection{Representativity of the day}
	The day the data was collected on (c.f. \Cref{sec: introduction}) is not mentioned. Therefore we cannot know, if it is representative. The people, asked to enter their movement, could had an exceptional day, like a vacation day, a doctors appointment or a broken car and therefore behave different from a usual day. \\
	Also the day itself is not mentioned, so we cannot determine, if it was even a working day or a weekendday. This influences the behaviour drastically.

@@

	\subsection{Individuality of lifestyle}
	Obviously, people are individual in their way of life. So there are people, with enough money to buy for example a car, but refuse to do so in order to reduce CO$_2$ emission, or simplydislike driving. On the other end of the spectrum, some people, who have little money, still own and drive a car daily in order to go to work, since they cannot afford an other apartment.\\
	One can think of multitude scenarios of people behaving different caused by their individuality.

	\subsection{Inverse behavior in a strata}
	As an example, take a look at the strata 6, which denotes the richest people considered. Their we have inter alia two groups: 
	\begin{enumerate}
		\setlength{\itemindent}{1cm}
		\item[1. Group]
		Hard working people, laboring 60+ hours per weak to earn their money. One can imagine that they have to move quite a lot since they are always busy.
		\item[2. Group]
		People, who are rich by birth, which do not have the necessity to work or move at all. They could possibly stay home and do not have to leave at all.
	\end{enumerate} 
	Those two groups are completely opposite, but still belong to the same strata. Now also considering strata 1, we can find the exact same movement behaviour in there as well. Within the poorest there are people that are wandering around the town via feet or bike, since they have no objective, like work. Also there are people, who do not move at all, because of the same reason.

	So we can see that based on the information we have, it is very unlikely to have a clear correlation between the given data and the strata. However, given more information about the previously mentioned aspects and more entries in general, a kind of correlation could be found.\\
	Future research could include a component analysis of the decision tree and neural network in order to ascertain the influencing parts and therefore improve the data gathering. Also one could use different network visualization tools in order to infer patterns. An example would be to take the origin (destination) sectors as nodes, an edge, if there is a movement between, directed or undirected, and a different thickness or color gradient, based on the number of this edge being taken.\\

	Overall we can conclude that with the data we got, we are not able to find a correlation.

>>>>

	\section{Discussion} \label{sec: discussion}
%	\begin{itemize}
%		\item repr. working day
%		\item over/under std's
%		\item indiv. of lifestyle
%		\item inv. behaviour in same strata
%	\end{itemize}
	Regarding the results, of not predicting the strata and also not observing any meaningful clusters throughout the data in given and stratified form, we come uo with various aspects having an impact on the data. We state 4 main influencing aspects, explaining the variance throughout the data.

	\subsection{Representativity of the day}
	The day the data was collected on (c.f. \Cref{sec: introduction}) is not mentioned. Therefore we do not know, if it is representative. The people, asked to enter their movement, could had an exceptional day, like a vacation day, a doctors appointment or a broken car and therefore behave different from an usual day. \\
	Also the day itself is not mentioned, so we cannot determine, if it was even a working day or a weekend day. This influences the behaviour drastically.

@@

	\subsection{Individuality of lifestyle}
	Obviously, people are individual in their way of life. So there are people, with enough money to buy for example a car, but refuse to do so in order to reduce CO$_2$ emission, or simply dislike driving. On the other end of the spectrum, some people, who have little money, still own and drive a car daily in order to go to work, since they cannot afford an other apartment.\\
	One can think of multitude scenarios of people behaving different caused by their individuality.

	\subsection{Inverse behavior in a strata}
	As an example, take a look at the strata 6, which denotes the richest people considered. Their we have inter alia two groups: 
	\begin{enumerate}
		\setlength{\itemindent}{1cm}
		\item[1. Group:]
		Hard working people, laboring 60+ hours per week to earn money. One can imagine that they have to move quite a lot since they are always busy.
		\item[2. Group:]
		People, who are rich by birth, which do not have the necessity to work or move at all. They could possibly stay home and do not have to leave at all.
	\end{enumerate} 
	Those two groups are completely opposite, but still belong to the same strata. Now also considering strata 1, we can find the exact same movement behaviour in there as well. Within the poorest there are people that are wandering around the town via feet or bike, since they have no objective, like work. Also there are people, who do not move at all, because of the same reason.

	So we can see that based on the information we have, it is very unlikely to have a clear correlation between the given data and the strata. However, given more information about the previously mentioned aspects and more entries a correlation can not be ruled out in general.\\
	Future research could include a component analysis of the decision tree and neural network in order to ascertain the influencing parts and therefore improve the data gathering. Also one could use different network visualization tools in order to infer patterns. An example would be to take the origin (destination) sectors as nodes, an edge, if there is a movement between, directed or undirected, and a different thickness or color gradient, based on the number of times this edge being taken.\\

	Overall we can conclude that with the data we get, we are not able to find a correlation.

### 2018-07-16 dokumentation/introduction.tex
Miriam hat keine Lust mehr

\section{Introduction} \label{sec: introduction}
	% could add more in depth 
	Within the time of Industry 4.0 and various data sources the question arises, if one can define who we are by the collected data? In particular is it possible to determine the wealth of a person, only given movements of one single day?
	For this we considered the dataset stated in \cite{rich_do_not_rise_early}. There we have a set of 124979 rows of movement data of various persons from the Columbian town Medellín, which is the second largest Colombian town with an estimated population of 2.5 million as of 2017 \cite{population_number} . All the data was collected at a single day, with possibly multiple entries referring to the same person.\\
	The data entries consist of data about the movement, like endpoints, length, and also some meta parameters like gender, age or the so-called strata of the person. The strata defines the socio-economic group, reflecting the affluence and therefore impose the ancillary costs. Those costs are defined by Colombians laws, which classifies households to regulate the access to public utility services, having as a result six socio-economic strata \cite{rich_do_not_rise_early}.\\
	Our goal is to ascertain, if there is a correlation between the movements and the strata, in order to be able to predict the strata based on the movements. This is done in two steps:\\
	First, by clustering using the k-means algorithm, considering different distance measures, with optionally including the principal component analysis (PCA).\\
	And second, a decision tree and neural net by training and testing.

>>>>

\section{Introduction} \label{sec: introduction}
	% could add more in depth 
	Within the time of Industry 4.0 and various data sources the question arises, if one can define who we are by the collected data. In particular, is it possible to determine the wealth of a person, only given movements of one single day?
	For this we considered the dataset stated in \cite{rich_do_not_rise_early}. There we have a set of 124979 rows of movement data of various persons from the Columbian town Medellín, which is the second largest Colombian town with an estimated population of 2.5 million as of 2017 \cite{population_number} . All the data was collected at a single day, with possibly multiple entries referring to the same person.\\
	The data entries consist of data about the movement, like endpoints, length, and also some meta parameters like gender, age or the so-called strata of the person. The strata defines the socio-economic group, reflecting the affluence and therefore impose the ancillary costs. Those costs are defined by Colombians laws, which classifies households to regulate the access to public utility services, having as a result six socio-economic stratas \cite{rich_do_not_rise_early}.\\
	Our goal is to ascertain, if there is a correlation between the movements and the strata, in order to be able to reproduce or predict the strata based on the movements. This is done in two steps:\\
	First, by clustering using the k-means algorithm, considering different distance measures, with optionally including the principal component analysis (PCA).\\
	And second, a decision tree and neural net by training and testing.

### 2018-07-16 dokumentation/neuralnet.tex
Miriam hat keine Lust mehr

\textbf{Neural Net} \label{subsec: neural net}\\
	In this section we want to further improve the accuracy of predicting the strata of one person by using neural networks. Like in the previous section, where we used decision trees, we need ground truth, in this case the strata, to be able to train the neural networks. For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{sec: proprocessing}).\\	
	We do this, because results on the normal datasets had an unacceptable performance, since only single movements and not complete paths of individuals are considered. An example training and performance measure is given in \Cref{fig: NN without vector}, where unprocessed data is used. The performance is measured using 10-fold cross validation, i.e. the data is split into 10 subsets, where in each iteration exactly one data set is used as test set and the other 9 as training set. The average value of the accuracy values leads to the total accuracy of the neural net.
	\begin{figure}[H]
		\vspace*{-1em}
		\centering
		\includegraphics[scale = 0.4]{src/pic/NN_without_vector.png}
		\caption{An example of a neural net trained without person vector data.}
		\label{fig: NN without vector}
	\end{figure}
	\vspace*{-1.5em}

	In the following we consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	As an example of other strata aggregation we combine the stratas 1--2, 3--4 and 5--6 together and call them $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$. This builds a superset of the original stratas and since the stratas themselves are logically connected this task should be easier to fulfill.\\

	For each neural net we are using equally distributed data sets with 100, 200 and the maximal amount of 595 individuals per strata which are provided by the \texttt{testDataGenerator} from \Cref{sec: proprocessing}. For every neural net and every set size we perform 5 independent runs and calculate the average over those accuracy values in order to have a sophisticated, comparable statement. 
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|}
			\hline
			&   \#    &        & \multicolumn{3}{c|}{Set size} \\
			Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
			$\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
			$\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
			$\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
			$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
			%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
			$\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
			$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
		\end{tabular}
		\caption{The accuracy values of the neural nets. (See excel-spreadsheet)}
		\label{tab: nn-accuracy}
		% mittels deep-learning-vector-average
	\end{figure}

	%TODO: recompute
	The size of larger nets in terms of neurons is counter-productive, since, if we take 50 neurons per layer, we have $14 \cdot 50^4 \cdot 6 \approxeq 525.000.000$ synapses for which the input dataset would be too small to perform sufficient training.\\

>>>>

\textbf{Neural Net} \label{subsec: neural net}\\
	In this section we want to further improve the accuracy of predicting the strata of one person by using neural networks. Like in the previous section, where we used decision trees, we need ground truth to be able to train the neural networks. For all the neural net computations we consider person vector data sets of different sizes (c.f. \Cref{sec: proprocessing}).\\	
	We do this, because results on the normal datasets had an unacceptable performance, since only single movements and not complete paths of individuals are considered. An example training and performance measure is given in \Cref{fig: NN without vector}, where unprocessed data is used. The performance is measured using 10-fold cross validation, i.e. the data is split into 10 subsets, where in each iteration exactly one data set is used as test set and the other 9 as training set. The average value of those accuracy values leads to the total accuracy of the neural net.

	In the following we consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	We call the aggregated strata sets $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$ denoting the number of neurons. This builds a superset of the original stratas and since the stratas themselves are logically connected, this task should be easier to fulfill.\\
		\begin{figure}[H]
		\vspace*{-1em}
		\centering
		\includegraphics[scale = 0.4]{src/pic/NN_without_vector.png}
		\caption{An example of a neural net trained without person vector data.}
		\label{fig: NN without vector}
	\end{figure}
	\vspace*{-1.5em}

	For each neural net we are using equally distributed data sets with 100, 200 and the maximal amount of 595 individuals per strata. For every neural net and every set size, we perform 5 independent runs and calculate the average over those accuracy values in order to have a sophisticated, comparable statement. 
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|}
			\hline
			&   \#    &        & \multicolumn{3}{c|}{Set size} \\
			Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
			$\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
			$\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
			$\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
			$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
			%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
			$\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
			$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
		\end{tabular}
		\caption{The accuracy values of the neural nets}
		\label{tab: nn-accuracy}
		% mittels deep-learning-vector-average
	\end{figure}

	%TODO: recompute
	The size of larger nets, in terms of neurons, is counter-productive, since, if we take 50 neurons per layer, we have $14 \cdot 50^4 \cdot 6 < 849 \cdot 50^4 \cdot 6 \approxeq 31.837.500.000$ synapses for which the input dataset would be too small to perform sufficient training.\\

### 2018-07-16 dokumentation/observation.tex
Miriam hat keine Lust mehr

\section{Conclusion} \label{sec: observation}
	%	TODO (1 page)
	%	TODO: restructure. Have like 3 parts
	%	The greater the population, the more the borders between the stratas blur. 
	As an overall result we get, that we can not determine the strata based on the information we have.
	Using various datasets (c.f. \Cref{sec: proprocessing}), we witnessed, that having equally distributed datasets leads to an overall higher accuracy. This rules out the bias observed in the original data, where strata 2 and 3 are very dominant (c.f. \Cref{table: distribution normal}), but also reduces the set size from originally 124978 to $6*2038=12228$ entries equally distributed over all stratas.\\
	During clustering we observed, that using a different distance measure formula would not lead to a huge difference. Also, we detected that reducing the numbers of clusters leads to better results, but decreases the significance of the statement, that could be made.\\
	Using a different neural net architecture will most likely not chance the accuracy value drastically. As stated, more complex nets need more training data, which is restricted for reasons mentioned above.\\
	What we can observe is, that using the stratified vectors, we are able to increase the performance and accuracy, but still have no sufficient predictions. Therefore we see, the more data we have, the higher the variance within the stratas. We cannot draw lines to distinguish between different stratas. Data points, which were outliers in the smaller sets, are now not considered to be outliers, because many others have the same characteristics. So the lines, we were able to draw for smaller datasets, are blurring.\\ %TODO: letzter satz doof	-> hihi

>>>>

\section{Conclusion} \label{sec: observation}
	%	TODO (1 page)
	%	TODO: restructure. Have like 3 parts
	%	The greater the population, the more the borders between the stratas blur. 
	As an overall result we observe, that we can not determine the strata based on the information we have.
	Using various datasets, we witness, that having equally distributed datasets leads to an overall higher accuracy. This rules out the bias observed in the original data, where strata 2 and 3 are very dominant (c.f. \Cref{table: distribution normal}), but also reduces the set size from originally 124978 to $6*2038=12228$ entries equally distributed over all stratas.\\
	During clustering we observe, that using a different distance measure formula would not lead to a huge difference. Also, we detect that reducing the number of clusters leads to better results, but decreases the significance of the statement, that could be made.\\
	Using a different neural net architecture will most likely not chance the accuracy value drastically. As stated, more complex nets need more training data, which is restricted for the reasons mentioned above.\\
	What we can observe is, that using the stratified vectors, we are able to increase the performance and accuracy, but still have no sufficient predictions. Therefore we see: the more data we have, the higher the variance within the stratas is. We cannot draw lines to distinguish between different stratas. Data points, which were outliers in the smaller sets, are now not considered to be outliers, because many others have the same characteristics. So the lines, we were able to draw for smaller datasets, are blurring.\\ %TODO: letzter satz doof	-> hihi

### 2018-07-16 dokumentation/preprocessing.tex
Miriam hat keine Lust mehr

\subsection{Preprocessing}\label{sec: proprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform some analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is 1 line defining a \texttt{NotANumber}-exception and therefore gets excluded from further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments, the script is able to create all test sets used by our clustering and neural net approaches.\\
	We observe the following distribution over the whole dataset:\\

@@

	\vspace*{-3em}
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6  & $\Sigma$ \\ \hline
			abs   & 3153 & 23367 & 21418 & 3497 & 2083 & 595 &  54113   \\
			\%   & 5.83 & 43.18 & 39.58 & 6.46 & 3.85 & 1.1 &   100
		\end{tabular}
		\vspace*{-2.5em}
	\end{figure}
	Following, we introduce vectors representing single persons. Since strata 6 is the smallest strata with 595 persons, it limits the size of an equally distributed dataset where each data point coincides with one person.\\

	\textbf{Stratified Person Data}\label{subsubsec: person vector data}\\
	As stated before, instead of simple IDs for every person we expand the parsing by using a data encapsulating in a class called \texttt{Person}. This class stores the ID, the parameters defining a person (c.f. \Cref{sec: proprocessing}), and all movements from that person.\\
	Then we are able to compute the following vector, with 850 entries, for further usage, that combines all movements of the person:
	\begin{align*}
	\underbrace{\#o_1, \dots, \#o_{413}, \#d_1, \dots, \#d_{413}}_{2\cdot 413} ,
	\underbrace{\mathit{AM}, \mathit{MD}, \mathit{PM}, \mathit{MN}}_{4}, 
	\underbrace{\#r_1, \dots, \#r_7}_{7}, \\
	\underbrace{\#\mathit{MoT}_1, \dots, \#\mathit{MoT}_7}_{7}, \underbrace{\mathit{S_{Dest}}, \mathit{S_{Dist}}, \mathit{G}, \mathit{A} ,\mathit{strata}, \mathit{strataGrouped}}_{6}
	\end{align*}
	with the following abbreviations ($1 \le i \le 413$, $1 \le j \le 7$):
	\begin{figure}[H]
		\centering
		\hspace*{-.3cm}
		\begin{subfigure}{0.50\textwidth}
		\begin{itemize}
			\setlength{\itemindent}{.4cm}
			\item[$o_i$:]  the $i$-th origin data point
			\item[$d_i$:]  the $i$-th destination data point
			\item[$\mathit{AM}$:] movements at time stamp AM
			\item[$\mathit{MD}$:] movements at time stamp MD
			\item[$\mathit{PM}$:] movements at time stamp PM
			\item[$\mathit{MN}$:] movements at time stamp MN
			\item[$r_j$:] the $j$-th reason
		\end{itemize}
	\end{subfigure}\hspace*{1cm}
	\begin{subfigure}{0.48\textwidth}
	\begin{itemize}
			\item[$\mathit{MoT}_j$:] the $j$-th mean of transportation
			\item[$\mathit{S_{Dest}}$:] sum of all durations
			\item[$\mathit{S_{Dist}}$:] sum of all distances
			\item[$\mathit{G}$:] the gender
			\item[$\mathit{A}$:] the age
			\item[$strata$:] the strata (used for comparison)
			\item[$strataGrouped$:] the aggregated stratas
		\end{itemize}
	\end{subfigure}
	\end{figure}

>>>>

\subsection{Preprocessing}\label{sec: proprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform some analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line encounter a \texttt{NotANumber}-exception and therefore gets excluded from further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments, the script is able to create all test sets used by our clustering and neural net approaches.\\
	We observe the following distribution over the whole dataset:\\

@@

	\vspace*{-3em}
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6  & $\Sigma$ \\ \hline
			abs   & 3153 & 23367 & 21418 & 3497 & 2083 & 595 &  54113   \\
			\%   & 5.83 & 43.18 & 39.58 & 6.46 & 3.85 & 1.1 &   100
		\end{tabular}
		\vspace*{-2.5em}
	\end{figure}
	Following, we introduce vectors representing single persons. Since strata 6 is the smallest strata with 595 persons, it limits the size of an equally distributed dataset, where each data point coincides with one person.\\

	Moreover, we define aggregated strata as the combination of strata 1 and 2 to "strata\_1", strata 3 and 4 to "strata\_2" and strata 5 and 6 to "strata\_3".

	\textbf{Stratified person data}\label{subsubsec: person vector data}\\
	As stated before, additionally of simple IDs for every person we expand the parsing by using a data encapsulating in a class called \texttt{Person}. This class stores the ID, the parameters defining a person, and all movements from that person.\\
	Then we are able to compute the following vector, with 850 entries, for further usage, that combines all movements of the person:
	\begin{align*}
	\underbrace{\#o_1, \dots, \#o_{413}, \#d_1, \dots, \#d_{413}}_{2\cdot 413} ,
	\underbrace{\mathit{AM}, \mathit{MD}, \mathit{PM}, \mathit{MN}}_{4}, 
	\underbrace{\#r_1, \dots, \#r_7}_{7}, \\
	\underbrace{\#\mathit{MoT}_1, \dots, \#\mathit{MoT}_7}_{7}, \underbrace{\mathit{S_{Dest}}, \mathit{S_{Dist}}, \mathit{G}, \mathit{A} ,\mathit{strata}, \mathit{strataGrouped}}_{6}
	\end{align*}
	with the following abbreviations ($1 \le i \le 413$, $1 \le j \le 7$):
	\begin{figure}[H]
		\centering
		\hspace*{-.3cm}
		\begin{subfigure}{0.50\textwidth}
		\begin{itemize}
			\setlength{\itemindent}{.4cm}
			\item[$o_i$:]  the $i$-th origin data point
			\item[$d_i$:]  the $i$-th destination data point
			\item[$\mathit{AM}$:] movements at time stamp AM
			\item[$\mathit{MD}$:] movements at time stamp MD
			\item[$\mathit{PM}$:] movements at time stamp PM
			\item[$\mathit{MN}$:] movements at time stamp MN
			\item[$r_j$:] the $j$-th reason
		\end{itemize}
	\end{subfigure}\hspace*{1cm}
	\begin{subfigure}{0.48\textwidth}
	\begin{itemize}
			\item[$\mathit{MoT}_j$:] the $j$-th mean of transportation
			\item[$\mathit{S_{Dest}}$:] sum of all durations
			\item[$\mathit{S_{Dist}}$:] sum of all distances
			\item[$\mathit{G}$:] the gender
			\item[$\mathit{A}$:] the age
			\item[$strata$:] the strata (used for comparison)
			\item[$strataGrouped$:] the aggregated stratas
		\end{itemize}
	\end{subfigure}
	\end{figure}
